---
title: "Select Functions"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Goal

In this project we will see the usage of select() function in R. It is a function of dplyr package. We will use the data set named [Undergraduate Admission Test Survey in Bangladesh.](https://www.kaggle.com/datasets/ahefatresearch/undergraduate-admission-test-survey-in-bangladesh)

First we need to install the necessary packages for this project and we will also upload the data.

### Upload the Data and Install Packages

```{r, error=FALSE, message=FALSE}
library(dplyr)
library(DT)
Data <- read.csv("C:/Users/yrabb/Downloads/Undergraduate Admission Test Survey in Bangladesh.csv")
```

This data set has 600 observations and 15 variables.

### Select Variables by Index Positions and Names

```{r}
Data%>%
  select(2,3)%>%
  datatable()
Data%>%
  select((c(2,3)))%>%
  datatable()
Data%>%
  select((c('Politics','University')))%>%
  datatable()
```

### Drop Variables and Select all Variables between Two Variables

```{r}
Data%>%select(-c('Politics', 'University'))%>%
  datatable()

Data%>%select(('Politics':'University'))%>%
  datatable()
```

### Select all Variables start and end with

```{r}
Data%>% select(starts_with('f'))%>%
  datatable()

Data%>% select(ends_with('s'))%>%
  datatable()
```

### Select Variables Containing Characters

```{r}
Data%>%select(contains('f'))%>%
  datatable()
Data%>%select_if(is.numeric)%>%
  datatable()

```
